Determinism, Complexity, and Predictability in Computer Performance

### 2014-02-07 unusedFigsTables.tex
working on the results/bib/and figures

@@

>>>>

\begin{table}[htdp]
\caption{ Embedding Parameters for reference if needed. }
\begin{center}
\begin{tabular}{|c|c|c|}
\hline
&$\tau$ & $m$ \\
\hline
gcc & 10& 13\\
col\_major  &2&12\\
SVD\_Full &  10  &  12 \\
SVD\_IPC\_Regime1 & 5 &14  \\
SVD\_IPC\_Regime2 & 10   &12  \\
SVD\_IPC\_Regime3 & 2   &9  \\
SVD\_IPC\_Regime4 &  3  & 11 \\
SVD\_IPC\_Regime5 &  23  & 10 \\
SVD\_IPC\_Regime6 &  30  & 12  \\
\hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

 Table~\ref{tab:pe} shows the permutation entropy results for the
 examples considered in this paper, with the nRMSPE prediction
 accuracies from the previous section included alongside for easy
 comparison.

 \begin{table}[htbp]
   % increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.3}
   \caption{TCM NRMSE and PE NORMS}
   \label{tab:table_example}
   \centering
   % Some packages, such as MDW tools, offer better commands for making tables
   % than the plain LaTeX2e tabular which is used here.
   \begin{tabular}{|c|c|c|c|c|c|}
     \hline
     TCM & NRMSE & $m=3$  &$m=4$&$m=5$&$m=6$\\
     \hline
     \tt{row\_major} & 0.0102 & 0.7900  &0.6751&0.5458&0.4491\\
     \hline
     \tt{col\_major} & 0.0055 & 0.6411  &0.5029&0.4515&0.3955 \\
     \hline
     \tt{403.gcc} & 0.0865 & 0.9954  &0.9916&0.9880&0.9835\\
     \hline
     \tt{482.sphinx3} & 0.1142 & 0.9958  &0.9913&0.9866&0.9802 \\
      \hline
   \end{tabular}
 \end{table}

%  \begin{table}[htbp]
%   % increase table row spacing, adjust to taste
%   %\renewcommand{\arraystretch}{1.3}
%   \caption{Cache-miss rate performance traces: prediction error
%     (nRMSPE) and permutation entropy}
%   \label{tab:TCMpe}
%   \centering
%   % Some packages, such as MDW tools, offer better commands for making tables
%   % than the plain LaTeX2e tabular which is used here.
%   \begin{tabular}{|c|c|c|c|c|c|}
%     \hline
%      & nRMSE   &$n=4$&$n=5$&$n=6$\\
%     \hline
%     \tt{row\_major}  & 0.0324  &0.6751&0.5458&0.4491\\
%     \hline
%     \tt{col\_major}  & 0.0080  &0.5029&0.4515&0.3955 \\
%     \hline
%     \tt{403.gcc}  & 0.1416  &0.9916&0.9880&0.9835\\
%     \hline
%     \tt{482.sphinx3}  & 0.2032  &0.9913&0.9866&0.9802 \\
%      \hline
%   \end{tabular}
% \end{table}

 \begin{table}[htbp]
   % increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.3}
   \caption{IPC NRMSE and PE NORMS}
   \label{tab:table_example}
   \centering
   % Some packages, such as MDW tools, offer better commands for making tables
   % than the plain LaTeX2e tabular which is used here.
   \begin{tabular}{|c|c|c|c|c|c|}
     \hline
     ipc & NRMSE & $n=3$  &$n=4$&$n=5$&$n=6$\\
     \hline
      \tt{row\_major} & 0.0095 & 0.9912  &0.9723&0.9354&0.8876\\
     \hline
      \tt{col\_major} & 0.0071 & 0.9428  &0.8356&0.7601&0.6880\\
     \hline
     \tt{403.gcc} & 0.1805 & 0.9918  &0.9862&0.9814&0.9764\\
     \hline
     \tt{482.sphinx3} & 0.2946 & 0.9978  &0.9951&0.9914&0.9849 \\
      \hline
   \end{tabular}
 \end{table}

%  \begin{table}[htbp]
%   % increase table row spacing, adjust to taste
%   %\renewcommand{\arraystretch}{1.1}
%   \caption{Processor load performance traces: prediction error
%     (nRMSPE) and permutation entropy}
%   \label{tab:IPCpe}
%   \centering
%   % Some packages, such as MDW tools, offer better commands for making tables
%   % than the plain LaTeX2e tabular which is used here.
%   \begin{tabular}{|c|c|c|c|c|}
%     \hline
%      & nRMSPE   &$n=4$&$n=5$&$n=6$\\
%     \hline
%      \tt{row\_major} & 0.0778  &0.9723&0.9354&0.8876\\
%     \hline
%      \tt{col\_major} & 0.0161   &0.8356&0.7601&0.6880\\
%     \hline
%     \tt{403.gcc} & 0.2033   &0.9862&0.9814&0.9764\\
%     \hline
%     \tt{482.sphinx3} & 0.3670 & 0.9951&0.9914&0.9849 \\
%      \hline
%   \end{tabular}
% \end{table}

 %  \begin{table}[htbp]
 %   \caption{Prediction error (in nRMSPE) and permutation entropy (for
 %     different wordlengths $n$}
 %   \label{tab:pe}
 %   \centering
 %   \begin{tabular}{|c|c|c|c|c|c|}
 %     \hline
 %      {\bf cache misses} & error   &$n=4$&$n=5$&$n=6$\\
 %     \hline
 %     \tt{row\_major}  & 0.0324  &0.6751&0.5458&0.4491\\
 %     \hline
 %     \tt{col\_major}  & 0.0080  &0.5029&0.4515&0.3955 \\
 %     \hline
 %     \tt{403.gcc}  & 0.1416  &0.9916&0.9880&0.9835\\
 %     \hline
 %     \tt{482.sphinx3}  & 0.2032  &0.9913&0.9866&0.9802 \\
 %      \hline
 %      \hline
 %      {\bf insts per cyc} & error   &$n=4$&$n=5$&$n=6$\\
 %     \hline
 %      \tt{row\_major} & 0.0778  &0.9723&0.9354&0.8876\\
 %     \hline
 %      \tt{col\_major} & 0.0161   &0.8356&0.7601&0.6880\\
 %     \hline
 %     \tt{403.gcc} & 0.2033   &0.9862&0.9814&0.9764\\
 %     \hline
 %     \tt{482.sphinx3} & 0.3670 & 0.9951&0.9914&0.9849 \\
 %      \hline
 %   \end{tabular}
 % \end{table}

  \begin{table}[htbp]
   % increase table row spacing, adjust to taste
   \renewcommand{\arraystretch}{1.3}
   \caption{Normalized root mean squared error (nRMSE) of 4000-point
     predictions of memory \& processor performance from different
     programs.}
   \label{tab:PredError}
   \centering
   % Some packages, such as MDW tools, offer better commands for making tables
   % than the plain LaTeX2e tabular which is used here.
%   \begin{tabular}{|c|c|c|c|c|c|}
%     \hline
%      & cache misses NRMSE & IPC NRMSE \\
%     \hline
%     \tt{row\_major}  & 0.0102  & 0.0095 \\
%          \hline
%     \tt{col\_major}  &0.0055& 0.0071 \\
%     \hline
%     \tt{403.gcc}  & 0.0865& 0.1805 \\
%          \hline
%     \tt{482.sphinx3} & 0.1142& 0.2946 \\
%      \hline
%   \end{tabular}
% \end{table}
   \begin{tabular}{|c|c|c|c|c|c|}
     \hline
      & cache miss rate & instrs per cycle \\
     \hline
     \tt{row\_major}  & 0.0324  & 0.0778 \\
          \hline
     \tt{col\_major}  &0.0080& 0.0161 \\
     \hline
     \tt{403.gcc}  & 0.1416& 0.2033 \\
          \hline
     \tt{482.sphinx3} & 0.2032& 0.3670 \\
      \hline
   \end{tabular}
 \end{table}

@@

%[[Joshua: It may be interesting to look at the PE as a function of
%prediction horizon. It is known to me that certain start and end
%locations in the prediction strategy result in different prediction
%accuracy. Is it the case that when the algorithm tanks it is also the
%case that PE of the **TEST**(the 10\% we cut off )is high? This may
%be a great way to illustrate the concept if it works... OR maybe do
%complexity of forward path in embedding space?]]  some notes about
%this looking at row Cache 1000 very good RMSPE 21.4167 m = 3 4 5 6
%1.4192 2.1286 2.5942 2.9230 row Cache 2000 very good RMSPE 19.0990 m
%= 3 4 5 6 1.4145 2.1305 2.5825 2.9095 so even better row Cache 2010
%RMSPE 19.9716 m = 3 4 5 6 1.4149 2.1311 2.5830 2.9096 row Cache 1990
%RMSPE 19.1465 So prediction Horizons ranked in order of best RMSPE
%RMSPE L 3 4 5 6 1st 19.0990 2000 1.4145 2.1305 2.5825 2.9095 2nd
%19.1465 1990 1.4151 2.1293 2.5803 2.9067 3rd 19.9716 2010 1.4149
%2.1311 2.5830 2.9096 3rd 21.4167 1000 1.4192 2.1286 2.5942 2.9230
%ipcgcc m = 3 pe = 1.7770 penorm = 0.9918 m= 4 pe = 3.1341 penorm =
%0.9862 m = 5 pe = 4.6985 penorm = 0.9814 m=6 pe = 6.4242 penorm =
%0.9764 m=7 pe = 8.2450 penorm = 0.9671 >> [pe penorm] =
%permCalc(gcc100TCM,5,1) pe = 4.7299 penorm = 0.9880 >> [pe penorm] =
%permCalc(gcc100TCM,6,1) pe = 6.4707 penorm = 0.9835
